---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rusdattendance

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/rusdattendance)](https://CRAN.R-project.org/package=rusdattendance)
<!-- badges: end -->

The basic idea that I am working on is to extract attendance data from [RUSD's Infinite Campus database](https://racinewi.infinitecampus.org).
There are several different ways to query the database because it contains both built-in reports and individual-level attendance tracking.
In a perfect world, I would have a table of student demographic data and another table of attendance, and then create my own joins and summaries. LOL ... nope.

The least-bad option appears to be the report that is reached along the menu path Attendance -> Reports -> ADM and ADA Detail.
"ADM" stands for "Average Daily Membership" and "ADA" stands for "Average Daily Attendance."
This approach can create CSV files, which are at least tractable-ish.
Each file corresponds to a year.
I asked for per-grade-level reports.
There are subtotals, and blank lines, separating the per-grade data for each school.


## Installation

You can install the released version of rusdattendance from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rusdattendance")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# library(rusdattendance)
## basic example code
```

